Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-23 docs/paper/paper.tex

\section{Library Overview}\label{sec:overview}
JavaScript developers are familiar with the concept of map, filter and reduce skeletons as language constructs. In JavaScript, \verb+Array+s have \verb+map+, \verb+filter+, and \verb+reduce+ functions and version 6 of the EcmaScript adds those same methods to \verb+TypedArray+s \cite{es6-ta}. For example, to multiply all the elements of an \verb+Array+ by two:
\medskip

@@

The API provided by p-j-s \cite{pjs-api} is very similar to the synchronous one that is provided by the language. The asynchronous nature of the operation is reflected by the fact that the call to \verb+seq+ returns a \verb+Promise+ (alternatively a callback could be passed as a parameter to it).

>>>>

\section{Library Overview}\label{sec:overview}
JavaScript developers are familiar with the concept of map, filter and reduce skeletons as language constructs. In JavaScript, \verb+Array+s have \verb+map+, \verb+filter+, and \verb+reduce+ functions and version 6 of the EcmaScript standard adds those same methods to \verb+TypedArray+s \cite{es6-ta}. For example, to multiply all the elements of an \verb+Array+ by two:
\medskip

@@

The API provided by p-j-s \cite{pjs-api} is very similar to the synchronous one that is provided by the language. The asynchronous nature of the operation is reflected by the fact that the call to \verb+seq+ returns a \verb+Promise+ \cite{promise} (alternatively a callback could be passed as a parameter to it).
